---
title: "Eating Out"
author: "Iven Santos"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The data comes from the 1998 General Social Survey answer this question

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

## Methods

response variable is categorical: dine out last week?yes or no

explanatory variable is race, it, too is a categorical variable.
so we use cat~cat

Inference: chi-squared and fisher exact tests

# Descripitive Summaries

## Graphical Summary

### barchart
```{r}
barchartGC(~eatout + race,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```

## Numerical summary

```{r}
table1 <- xtabs(~eatout + race, data=mydata)
rowPerc(table1)
colPerc(table1)
```

this table shows that white people live closer to fast food chains.


# Results

## inferential results

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```


```{r}
fisherXY(mydata$race,mydata$eat)
```
For both charts whites go to eat out far more than the other races. maybe because they don't know how to cook. 
